### 2014-06-19 kypchak-morphfest-2014/poster.tex
last night's work
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@54635 72bbbca6-d526-0410-a7d9-f06f51895060

		\headerbox{Categorisation}{name=adjectives,column=4,below=devel}{
		%\headerbox{Morphophonology}{name=morphophon,below=morphtrans}{
			\htwo{Adjectives}
			\begin{itemize}
				\item morphologically distinct adjective classes
				\item most sources:\ adjectives can be used substantively and adverbially
				\item Other Turkic transducers:\ \texttt{0}-derivation (\hilitetwo{overgenerates})
				\item but not all adjectives have all of the following:\\
				comparative forms, substantive readings, adverbial readings
				\item Our approach:\ categorisation 
				\item only correct forms are analysed and generated
			\end{itemize}

		\scalebox{0.7}{
			\begin{tabular}{lllll}
				\toprule
				\textbf{Type} & \textbf{Gloss} & {\small \texttt{\tag{adj}(\tag{comp})}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{subst}}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{advl}}} \\
				\midrule
				\textbf{A1} & \eng{good} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} \\
				\textbf{A2} & \eng{old} & {\qipa иске (искерәк)} & {\qipa иске (искерәк)} & {\qipa — (—)} \\
				\textbf{A3} & \eng{dead} & {\qipa үле (—)} & {\qipa үле (—)} & {\qipa — (—)} \\
				\textbf{A4} & \eng{basic} & {\qipa төп (—)} & {\qipa — (—)} & {\qipa — (—)} \\
				\bottomrule
			\end{tabular}
		}
	}

@@

>>>>

		\headerbox{Categorisation}{name=adjectives,column=4,below=devel}{
		%\headerbox{Morphophonology}{name=morphophon,below=morphtrans}{
			\htwo{Adjectives}
			\begin{itemize}
				\item morphologically distinct adjective classes
				\item most sources:\ adjectives can be used substantively and adverbially
				\item Other Turkic transducers:\ \texttt{0}-derivation (\hilitetwo{overgenerates})
				\item but not all adjectives have all of the following:\\
				comparative forms, substantive readings, adverbial readings
				\item Our approach:\ categorisation 
				\item if properly categorised, only correct forms are analysed and generated
			\end{itemize}

		\scalebox{0.7}{
			\begin{tabular}{lllll}
				\toprule
				\textbf{Type} & \textbf{Gloss} & {\small \texttt{\tag{adj}(\tag{comp})}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{subst}}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{advl}}} \\
				\midrule
				\textbf{A1} & \eng{good} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} \\
				\textbf{A2} & \eng{old} & {\qipa иске (искерәк)} & {\qipa иске (искерәк)} & {\qipa — (—)} \\
				\textbf{A3} & \eng{dead} & {\qipa үле (—)} & {\qipa үле (—)} & {\qipa — (—)} \\
				\textbf{A4} & \eng{basic} & {\qipa төп (—)} & {\qipa — (—)} & {\qipa — (—)} \\
				\bottomrule
			\end{tabular}
		}

		\htwo{Adverbs}
			\begin{itemize}
				\item Certain time adverbs have special attributive and genetive forms\\
				бүгүн, быйыл, кече, жана, 
			\end{itemize}

@@

		\headerbox{Other uses}{name=uses,column=1,below=morphophon}{
			\begin{itemize}
				\item HFST transducers are trivially converted to \textbf{spell checkers}
				\item Segmenter, e.g.\ {\qipa көрүшкөндөрүмдөнсүңбү} :\\
				 {\small \texttt{көр\hilitegrey{>}\{I\}ш\hilitegrey{>}\{G\}\{A\}н\hilitegrey{>}\{L\}\{A\}р\hilitegrey{>}\{I\}м\hilitegrey{>}\{D\}\{A\}н\hilitegrey{>}с\{I\}ң\hilitegrey{>}\{B\}\{I\}}}
			\end{itemize}
		}
